Modal Abstractions for Virtualizing Memory Addresses

### 2024-07-24 examples.tex
added level to the extended inv

\begin{figure*}
\footnotesize
\[
\begin{array}{l}
  \mathcal{I}\textsf{ASpace}_{\textsf{id}}(\ptablestore,\Xi,m)\stackrel{\triangle}{=} \textsf{ASpace\_Lookup}_{\textsf{id}}(\ptablestore,\Xi,m) \ast \mathsf{GhostMap}(\mathsf{id},\Xi)\ast\\
  \left(\bigast{(\vaddr, \textsf{paddr})\in \ptablestore}{\exists\;(\textsf{l4e, l3e, l2e, l1e, paddr})\ldotp \textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}(\vaddr\textsf{, l4e, l3e, l2e, l1e, paddr})}\right)\ast \\
  \bigast{(\paddr,\mathsf{T}) \in \Xi}{\exists\; (\textsf{qfrac, q, val,}\vaddr) \ldotp \ulcorner \vaddr = \paddr + \textsf{KERNBASE} \urcorner \ast  \underbrace{\fracghostmaptoken{\delta}{\vaddr}{\paddr}{\qfrac} }_\text{Ghost translation} \ast \underbrace{\paddr \mapsto_{\mathsf{p}}\{\textsf{qfrac}\}\; \vale}_\text{Physical location}} \ast\\
   \qquad\underbrace{ \ulcorner \textsf{qfrac} = 1 \leftrightarrow \; \lnot\textsf{entry\_present }(\vale) \urcorner}_\text{Entry validity}\ast 
    \underbrace{\left(\ulcorner\textsf{entry\_present}(\vale)\urcorner \wand \forall_{\textsf{i}\in\textsf{0..511}} \ldotp \ghostmaptoken{\textsf{id}}{((\mathsf{entry\_page}\;\vale) + \textsf{i * 8})}{\_}\right)}_{\text{Indexing into next level of tables}} \\
  \textsf{ where } \\
   \textsf{ASpace\_Lookup}_{\textsf{id}}(\ptablestore,\Xi,m) \stackrel{\triangle}{=} \lambda\textsf{ cr3val} \ldotp \; \exists \gammaPred \; \ldotp \ulcorner m \; !!\; \textsf{cr3val} = \textsf{Some } \gammaPred \urcorner \ast
   % \ownGhost\gammaPred{\authfull{\ptableabswalk\ptablestore}} \ast  \ownGhostpv\gammaPred{\authfull{\pvmapping\Xi}}
   \ptableabswalk{\delta,\ptablestore} \ast \pvmapping{\delta,\Xi}

>>>>

\begin{figure*}
\footnotesize
\[
\begin{array}{l}
  \mathcal{I}\textsf{ASpace}_{\textsf{id}}(\ptablestore,\Xi,m)\stackrel{\triangle}{=} \textsf{ASpace\_Lookup}_{\textsf{id}}(\ptablestore,\Xi,m) \ast \mathsf{GhostMap}(\mathsf{id},\Xi)\ast\\
  \left(\bigast{(\vaddr, \textsf{paddr})\in \ptablestore}{\exists\;(\textsf{l4e, l3e, l2e, l1e, paddr})\ldotp \textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}(\vaddr\textsf{, l4e, l3e, l2e, l1e, paddr})}\right)\ast \\
  \bigast{(\paddr,\mathsf{level}) \in \Xi}{\exists\; (\textsf{qfrac, q, val,}\vaddr) \ldotp \ulcorner \vaddr = \paddr + \textsf{KERNBASE} \; \textsf{level} > 1\urcorner \ast  \underbrace{\fracghostmaptoken{\delta}{\vaddr}{\paddr}{\qfrac} }_\text{Ghost translation} \ast \underbrace{\paddr \mapsto_{\mathsf{p}}\{\textsf{qfrac}\}\; \vale}_\text{Physical location}} \ast\\
   \qquad\underbrace{ \ulcorner \textsf{qfrac} = 1 \leftrightarrow \; \lnot\textsf{entry\_present }(\vale) \urcorner}_\text{Entry validity}\ast 
    \underbrace{\left(\ulcorner\textsf{entry\_present}(\vale)\urcorner \wand \forall_{\textsf{i}\in\textsf{0..511}} \ldotp \ghostmaptoken{\textsf{id}}{((\mathsf{entry\_page}\;\vale) + \textsf{i * 8})}{\textsf{level-1}}\right)}_{\text{Indexing into next level of tables}} \\
  \textsf{ where } \\
   \textsf{ASpace\_Lookup}_{\textsf{id}}(\ptablestore,\Xi,m) \stackrel{\triangle}{=} \lambda\textsf{ cr3val} \ldotp \; \exists \gammaPred \; \ldotp \ulcorner m \; !!\; \textsf{cr3val} = \textsf{Some } \gammaPred \urcorner \ast
   % \ownGhost\gammaPred{\authfull{\ptableabswalk\ptablestore}} \ast  \ownGhostpv\gammaPred{\authfull{\pvmapping\Xi}}
   \ptableabswalk{\delta,\ptablestore} \ast \pvmapping{\delta,\Xi}
